An exact Riemann solver for multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state

### 2019-06-03 Manuscript.tex
w2

\documentclass[review]{elsarticle}
\usepackage{amssymb}
%\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{color}
%\usepackage{tikz}
%\usetikzlibrary{arrows,shapes}
%\usetikzlibrary{shapes.geometric}
%\usetikzlibrary{arrows.meta}
\usepackage{authblk}
\usepackage{graphics,graphicx}
\usepackage{mathrsfs}
\usepackage{amsmath,bm}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{listings}
\usepackage{setspace}
\graphicspath{{TikzFig/}{Picture/}}
\usepackage{hyperref}

%\journal{Journal of Computational Physics}
\bibliographystyle{elsarticle-num}

@@

\emph{\textbf{Left-going rarefaction wave} }
Across the left wave associated with $\lambda_3$-wave, ($\lambda_3=u-c_e$), we have
\begin{equation}
  \frac{d\rho}{1} = \frac{d(\rho u)}{u-c_e} = \frac{d(\rho E)}{h-uc_e} = \frac{ds_{xx}}{-\frac{4\mu}{3}\frac{1}{\rho}}.
\end{equation}
which lead to 
\begin{align}
  \label{eq:urho}
  & \text{d} u =-\frac{c_e}{\rho}\text{d}\rho,\\
 \label{eq:Erho}
  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho.\\
\label{eq:sxxrho}
& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho,
\end{align}
Take the relation of EOS (\ref{eq:mie}) in, we can get the pressure  as
\begin{equation}
  dp =  \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho,
\end{equation}
it can be written as a differential equation of $p(\rho)$
\begin{equation}
  p'(\rho) - \lambda_1 \frac{p}{\rho^2} = f_2(\rho),
\end{equation}
where 
\begin{equation}
  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
\end{equation}
The pressure can be solved out as 
\begin{equation}\label{eq:p_rho}
  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
\end{equation}
Then for a given density $\rho$, we can get  the sonic speed $c_e$  and velocity 
\begin{equation}
  u+\int\frac{c_e}{\rho} d\rho = \text{constant}.
\end{equation}

\emph{\textbf{Right-going rarefaction wave} }
Across the right wave associated with $\lambda_4$-wave, ($\lambda_3=u+c_e$), we have
\begin{equation}
  \frac{d\rho}{1} = \frac{d(\rho u)}{u+c_e} = \frac{d(\rho E)}{h+uc_e} = \frac{ds_{xx}}{-\frac{4\mu}{3}\frac{1}{\rho}}.
\end{equation}
which lead to 
\begin{align}
  \label{eq:urho}
  & \text{d} u =\frac{c_e}{\rho}\text{d}\rho,\\
 \label{eq:Erho}
  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho.\\
\label{eq:sxxrho}
& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho,
\end{align}
We can get  similar  relations  as the left-going wave as
\begin{equation}
  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
\end{equation}
\begin{equation}
  u-\int\frac{c_e}{\rho} d\rho = \text{constant}.
\end{equation}

@@

\emph{\textbf{Left-going rarefaction wave} }
Across the left wave associated with $\lambda_2$-wave, ($\lambda_2=u-c_p$), we have
\begin{equation}
  \frac{d\rho}{1} = \frac{d(\rho u)}{u-c_p} = \frac{d(\rho E)}{h-uc_p}.
\end{equation}
Samilar to section \ref{sec:rarefaction}, we can get the relations
\begin{equation}\label{eq:p_rhop}
  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
\end{equation}
and
\begin{equation}
  u+\int\frac{c_p}{\rho} d\rho = \text{constant},
\end{equation}
where
\begin{equation}
  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
\end{equation}
\emph{\textbf{Right-going rarefaction wave} }
Across the right wave associated with $\lambda_3$-wave, ($\lambda_3=u+c_e$), we have
\begin{equation}
  \frac{d\rho}{1} = \frac{d(\rho u)}{u+c_p} = \frac{d(\rho E)}{h+uc_p}.
\end{equation}
We can get  similar  relations  as the left-going wave as
\begin{equation}
  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
\end{equation}
\begin{equation}
  u-\int\frac{c_p}{\rho} d\rho = \text{constant}.
\end{equation}
\subsubsection{Relations across  shock waves}\label{sec:shockp}
By a same deducing process with Section \ref{sec:shock}, we can get the state after a shock as  
\begin{equation}
  s_{xx2} = s_{xx1},
\end{equation}
\begin{equation}\label{eq:shockp}
  p_2= \frac{2t(c_1f(\rho_2/\rho_0)+e_1)-(\sigma_1+s_{xx2})}{2tc_0-1},
\end{equation}
where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$.
\begin{equation}
  \sigma_2 = -p_2 +s_{xx2}.
\end{equation}
\begin{equation}\label{eq:shockup}
  u_2 = \left\{ \begin{aligned}
	 & u_1 - \sqrt{\frac{\sigma_1- \sigma_2}{t}} \quad \text{Left-going}, \\
	 & u_1 + \sqrt{\frac{\sigma_1- \sigma_2}{t}} \quad \text{Right-going}.
	\end{aligned}
	\right.
  \end{equation}
And the shock speed is given as 
\begin{equation}
  s = \frac{\rho_2u_2-\rho_1u_1}{\rho_2-\rho_1}.
\end{equation}

@@

\begin{figure}
  \centering
  \subfigure[Elastic rarefaction wave]{
	\label{fig:subfigure:a}
  \includegraphics[width=3.8cm]{Tikz-figure0.eps}}
  \subfigure[Plastic rarefaction wave]{
	\label{fig:subfigure:b}
  \includegraphics[width=3.8cm]{Tikz-figure1.eps}}
  \subfigure[Both elastic and plastic rarefaction waves]{
	\label{fig:subfigure:c}
  \includegraphics[width=3.8cm]{Tikz-figure2.eps}}
  \subfigure[ Elastic shock wave]{
	\label{fig:subfigure:d}
  \includegraphics[width=3.8cm]{Tikz-figure3.eps}}
  \subfigure[Plastic shock wave]{
	\label{fig:subfigure:e}
  \includegraphics[width=3.8cm]{Tikz-figure4.eps}}
  \subfigure[Both elastic and plastic shock waves]{
	\label{fig:subfigure:f}
	\includegraphics[width=3.8cm]{Tikz-figure5.eps}}
  \caption{The possible cases of Riemann solution structures in the left side.}
  \label{fig:cases}
\end{figure}

%
%There are mainly five  steps in the soluting process. 
%\begin{enumerate}
%  \item In section (\ref{sec:eva}), a pre-evaluation is done with a shock-contact-shock waves assumption to give an initial values of $\rho^*_L$ and $\rho^*_R$.  
%
%  \item  With  given $\rho^*_L$ and $\rho^*_R$, we need to  detect the left cases in Fig.\ref{fig:cases} and the corresponding right cases, this is done in section \ref{sec:eva}.
%
%  \item  We solve functions $s_{xx}(\rho)$, $p(\rho)$ and $u(\rho)$ for  different cases in section \ref{sec:one}.
%
%\item At last,   with  the informations in Section \ref{sec:contact},  
%\begin{equation}\label{eq:fus}
%  \begin{aligned}
%	f_u(\rho^*_L,\rho^*_R) = u_L^* -u_R^* = 0,\\
%	f_\sigma(\rho^*_L,\rho^*_R) = \sigma_L^* -\sigma_R^* = 0,
%\end{aligned}
%\end{equation}
% use a Newton iteration method to  get new $\rho^*_L$ and $\rho^*_R$, then do steps 2-5 again until the result convergents. this process is given in Section \ref{sec:iteration}.
%\end{enumerate}

  \subsection{The solving process}\label{sec:iteration}
  By the relations in Section  \ref{sec:Riemann}, all  variables can be written as functions of  the density, so if  densities in regions $\mathbf{R}^*_L$ and  $\mathbf{R}^*_R$ are known, the Riemann problem is solved.

@@

	\textbf{Initial:}

@@

\item 
\end{enumerate}

\textbf{Iteration begin:}
\begin{enumerate}[Step 1]
  \item Case select
	By a given  $\rho _{L,(k)}$ and a  $\rho _{R,(k)}$ in $k$ iteration step, we need to determine the case of the wave structures in the left and right. The determine process is done in Section \ref{sec:deter}.

  \item After determining the structure case, we need solve the Cauchy stresses and the velocities in regions $\mathbf{R}^*_L$ and $\mathbf{R}^*_L$, this is given in Section \ref{sec:functions}.

  \item  new 
The Newton iteration to evaluate $\rho_L^*$ and $\rho_R^*$ is given as
\begin{equation}
\left[ \begin{array}{l}
 \rho _{L,(k+1)}^*\\
\rho_{R,(k+1)}^*\\
\end{array}
\right] = 
\left[ \begin{array}{l}
 \rho _{L,(k)}^*\\
\rho_{R,(k)}^*\\
\end{array}
\right]-
\left[ \begin{array}{ll}
\frac{\partial f_{u(k)}}{\partial \rho_L^*} & \frac{\partial f_{u(k)}}{\partial \rho_R^*}\\
\frac{\partial f_{\sigma(k)}}{\partial \rho_L^*} & \frac{\partial f_{\sigma(k)}}{\partial \rho_R^*}\\
\end{array}
\right]^{-1}
\left[ \begin{array}{l}
f_{u(k)}\\
f_{\sigma(k)}\\
\end{array}
\right]
\end{equation}

The initial of densities are given as 
\begin{equation}
  \rho_{L(0)}^* = \rho_L \quad \rho_{R(0)}^* = \rho_R.
\end{equation}
The  convergence is meassured by 
\begin{equation}
\text{CHA} = \text{max} \left[  
\frac{|\rho_{L(k+1)}^*- \rho_{L,(k)}^*|}{\frac{1}{2}|\rho_{L(k+1)}^*+\rho_{L(k)}^*|},   \frac{|\rho_{R(k+1)}^*- \rho_{R,(k)}^*|}{\frac{1}{2}|\rho_{R(k+1)}^*+\rho_{R(k)}^*|},|f_{u}|,|f_{\sigma}|\right].
\end{equation}
and the tolerance is taken as $\text{TOL} = 10^{-4}$. It usually takes 3-4 step to get a convergence result.

The derivatives of $f_{u}$ and $f_{\sigma}$ are given by
\begin{equation}
  \frac{\partial f_{u,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u,(k+1)}-f_{u,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},\quad
  \frac{\partial f_{\sigma,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{\sigma,(k+1)}-f_{\sigma,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},
\end{equation}
At the first step, we use a simple  numerical difference  method
\begin{equation}
  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},\quad
  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},
\end{equation}
where $\Delta \rho$ is a little quatity, we can choose it as
\begin{equation}
  \Delta \rho_{L(R)} = \frac{\rho_{L(R),(0)}^*}{100}.
\end{equation}

A flow chat of this process is shown in Fig.\ref{fig:newton}.
\subsection{Pre-evaluation of densities}\label{sec:eva}
At first, we assume that there are only one elastic shock wave in the left side and another one  elastic shock in the right side as shown in Fig.\ref{fig:HLLC}. According to the conservation relations across the shocks, we have    
\begin{equation}
  \left\{
  \begin{aligned}
	&\hat{\rho}_L\hat{u}^*_L = \rho_L u_L +s_L(\hat{\rho}_L^*-\rho_L), \\
	&\hat{\rho}_L\hat{u}_L^{*2}-\sigma_L^* = \rho_L u_L^2 -\sigma_L +s_L(\hat{\rho}_L^* \hat{u}_L^*-\rho_L u_L), 
  \end{aligned}
\right.
\end{equation}
and
\begin{equation}
  \left\{
  \begin{aligned}
	&\hat{\rho}_R\hat{u}^*_R = \rho_R u_R +s_R(\hat{\rho}_R^*-\rho_R), \\
	&\hat{\rho}_R\hat{u}_R^{*2}-\sigma_R^* = \rho_R u_R^2 -\sigma_R +s_R(\hat{\rho}_R^* \hat{u}_R^*-\rho_R u_R). 
  \end{aligned}
\right.
\end{equation}
\begin{figure}
  \centering
  \includegraphics[width=8cm]{Tikz-figure7.eps}
  \caption{Pre-evaluation with a three-waves structure.}
  \label{fig:HLLC}
\end{figure}

Using the relation across the interface,
\begin{equation}
  \hat{u}_L^* = \hat{u}_R^* =\hat{s}^*,\quad \hat{\sigma}_L^* = \hat{\sigma}_R^*.
\end{equation}
the speed of contact wave can be evaluated as 
\begin{equation}
\hat{s}^* = \frac{\sigma_L-\sigma_R+\rho_L u_L(s_L-u_L)-\rho_R u_R(s_R-u_R)}{\rho_L(s_L-u_L)-\rho_R(s_R-u_R)},
\end{equation}
the density is solved as 
\begin{equation}
\hat{\rho}_L^* = \frac{\rho_L(u_L-s_L)}{\hat{s}^*-s_L}, \quad
\hat{\rho}_R^* = \frac{\rho_R(u_R-s_R)}{\hat{s}^*-s_R}.
\end{equation}
Here we define the speeds of left and right going waves as
 \begin{equation}
      s_L = \text{min} (u_L-c_L, u_R-c_R, 0),  \quad s_R = \text{max}(u_L+c_L, u_R+c_R, 0).
\end{equation}
\subsection{Determining the case of structures} \label{sec:deter}

@@

\subsection{Functions of the pressure, derivative stress and velocity}\label{sec:functions}
\subsubsection{State in $\tilde{\mathbf{Q}}_{L(R)}$ in cases (c,f)}

>>>>

\documentclass[review]{elsarticle}
\usepackage{amssymb}
%\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{color}
%\usepackage{tikz}
%\usetikzlibrary{arrows,shapes}
%\usetikzlibrary{shapes.geometric}
%\usetikzlibrary{arrows.meta}
\usepackage{authblk}
\usepackage{graphics}
\usepackage{mathrsfs}
\usepackage{amsmath,bm}
\usepackage{subfigure}
\usepackage{caption,subcaption}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{listings}
\usepackage{setspace}
\graphicspath{{TikzFig/}{Picture/}}
\usepackage{hyperref}
\usepackage{stackengine}
\usepackage[demo]{graphicx}
%\journal{Journal of Computational Physics}
\bibliographystyle{elsarticle-num}

@@

\emph{\textbf{Left-going rarefaction wave} }
Across the left wave associated with $\lambda_3$-wave, ($\lambda_3=u-c_e$), we have
\begin{equation}
  \frac{d\rho}{1} = \frac{d(\rho u)}{u-c_e} = \frac{d(\rho E)}{h-uc_e} = \frac{ds_{xx}}{-\frac{4\mu}{3}\frac{1}{\rho}}.
\end{equation}
which lead to 
\begin{align}
  \label{eq:urho}
  & \text{d} u =-\frac{c_e}{\rho}\text{d}\rho,\\
 \label{eq:Erho}
  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho.\\
\label{eq:sxxrho}
& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho,
\end{align}
Take the relation of EOS (\ref{eq:mie}) in, we can get the pressure  as
\begin{equation}
  dp =  \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho,
\end{equation}
it can be written as a differential equation of $p(\rho)$
\begin{equation}
  p'(\rho) - \lambda \frac{p}{\rho^2} = f_2(\rho),
\end{equation}
where 
\begin{equation}
  \lambda = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda\frac{s_{xx}(\rho)}{\rho^2}.
\end{equation}
The pressure can be solved out as 
\begin{equation}\label{eq:p_rho}
  p e^{\frac{\lambda}{\rho}} - \int f_2(\rho) e^{\frac{\lambda}{\rho}}d\rho = \text{constant}.
\end{equation}
Then for a given density $\rho$, we can get  the sonic speed $c_e$  and velocity 
\begin{equation}
  u+\int\frac{c_e}{\rho} d\rho = \text{constant}.
\end{equation}

\emph{\textbf{Right-going rarefaction wave} }
Across the right wave associated with $\lambda_4$-wave, ($\lambda_3=u+c_e$), we have
\begin{equation}
  \frac{d\rho}{1} = \frac{d(\rho u)}{u+c_e} = \frac{d(\rho E)}{h+uc_e} = \frac{ds_{xx}}{-\frac{4\mu}{3}\frac{1}{\rho}}.
\end{equation}
which lead to 
\begin{align}
  \label{eq:urho}
  & \text{d} u =\frac{c_e}{\rho}\text{d}\rho,\\
 \label{eq:Erho}
  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho.\\
\label{eq:sxxrho}
& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho,
\end{align}
We can get  similar  relations  as the left-going wave as
\begin{equation}
  p e^{\frac{\lambda}{\rho}} - \int f_2(\rho) e^{\frac{\lambda}{\rho}}d\rho = \text{constant}.
\end{equation}
\begin{equation}
  u-\int\frac{c_e}{\rho} d\rho = \text{constant}.
\end{equation}

@@

\emph{\textbf{Left-going rarefaction wave} }
Across the left wave associated with $\lambda_2$-wave, ($\lambda_2=u-c_p$), we have
\begin{equation}
  \frac{d\rho}{1} = \frac{d(\rho u)}{u-c_p} = \frac{d(\rho E)}{h-uc_p}.
\end{equation}
Samilar to section \ref{sec:rarefaction}, we can get the relations
\begin{equation}\label{eq:p_rhop}
  p e^{\frac{\lambda}{\rho}} - \int f_2(\rho) e^{\frac{\lambda}{\rho}}d\rho = \text{constant}.
\end{equation}
and
\begin{equation}
  u+\int\frac{c_p}{\rho} d\rho = \text{constant},
\end{equation}
where
\begin{equation}
  \lambda = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda\frac{s_{xx}(\rho)}{\rho^2}.
\end{equation}
\emph{\textbf{Right-going rarefaction wave} }
Across the right wave associated with $\lambda_3$-wave, ($\lambda_3=u+c_e$), we have
\begin{equation}
  \frac{d\rho}{1} = \frac{d(\rho u)}{u+c_p} = \frac{d(\rho E)}{h+uc_p}.
\end{equation}
We can get  similar  relations  as the left-going wave as
\begin{equation}
  p e^{\frac{\lambda}{\rho}} - \int f_2(\rho) e^{\frac{\lambda}{\rho}}d\rho = \text{constant}.
\end{equation}
\begin{equation}
  u-\int\frac{c_p}{\rho} d\rho = \text{constant}.
\end{equation}
\subsubsection{Relations across  shock waves}\label{sec:shockp}
By a same deducing process with Section \ref{sec:shock}, we can get the state after a shock as  
\begin{equation}
  s_{xx2} = s_{xx1},
\end{equation}
\begin{equation}\label{eq:shockp}
  p_2= \frac{2t(c_1f(\rho_2/\rho_0)+e_1)-(\sigma_1+s_{xx2})}{2tc_0-1},
\end{equation}
where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$.
\begin{equation}
  \sigma_2 = -p_2 +s_{xx2}.
\end{equation}
\begin{equation}\label{eq:shockup}
  u_2 = \left\{ \begin{aligned}
	 & u_1 - \sqrt{\frac{\sigma_1- \sigma_2}{t}} \quad \text{Left-going}, \\
	 & u_1 + \sqrt{\frac{\sigma_1- \sigma_2}{t}} \quad \text{Right-going}.
	\end{aligned}
	\right.
  \end{equation}
And the shock speed is given as 
\begin{equation}
  s = \frac{\rho_2u_2-\rho_1u_1}{\rho_2-\rho_1}.
\end{equation}

@@

\begin{figure}
\captionsetup[subfigure]{labelformat=empty}
  \centering
  \subfigure[Elastic rarefaction wave $R^E$]{
	\label{fig:subfigure:a}
  \includegraphics[width=3.8cm]{Tikz-figure0.eps}}
  \subfigure[Plastic rarefaction wave]{
	\label{fig:subfigure:b}
  \includegraphics[width=3.8cm]{Tikz-figure1.eps}}
  \subfigure[Both elastic and plastic rarefaction waves]{
	\label{fig:subfigure:c}
  \includegraphics[width=3.8cm]{Tikz-figure2.eps}}
  \subfigure[ Elastic shock wave]{
	\label{fig:subfigure:d}
  \includegraphics[width=3.8cm]{Tikz-figure3.eps}}
  \subfigure[Plastic shock wave]{
	\label{fig:subfigure:e}
  \includegraphics[width=3.8cm]{Tikz-figure4.eps}}
  \subfigure[Both elastic and plastic shock waves]{
	\label{fig:subfigure:f}
	\includegraphics[width=3.8cm]{Tikz-figure5.eps}}
  \caption{The possible cases of Riemann solution structures in the left side.}
  \label{fig:cases}
\end{figure}

%\begin{figure}
%  \centering
%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure0.eps}}{\tiny ($\!R^\!E\!$) Elastic rarefaction}%
%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure1.eps}}{\tiny ($\!R^\!P\!$) Plastic rarefaction}
%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure2.eps}}{\tiny ($\!R\!^E\!R\!^P\!$) Both elastic and plastic rarefactions}
%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure3.eps}}{\tiny ($\!S^\!E$) Elastic shock}%
%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure4.eps}}{\tiny ($\!S^\!P\!$) Plastic shock}
%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure5.eps}}{\tiny ($\!S\!^E\!S\!^P\!$) Both elastic and plastic shocks}
%\caption{November to April}
%\end{figure}

%There are mainly five  steps in the soluting process. 
%\begin{enumerate}
%  \item In section (\ref{sec:eva}), a pre-evaluation is done with a shock-contact-shock waves assumption to give an initial values of $\rho^*_L$ and $\rho^*_R$.  
%
%  \item  With  given $\rho^*_L$ and $\rho^*_R$, we need to  detect the left cases in Fig.\ref{fig:cases} and the corresponding right cases, this is done in section \ref{sec:eva}.
%
%  \item  We solve functions $s_{xx}(\rho)$, $p(\rho)$ and $u(\rho)$ for  different cases in section \ref{sec:one}.
%
%\item At last,   with  the informations in Section \ref{sec:contact},  
%\begin{equation}\label{eq:fus}
%  \begin{aligned}
%	f_u(\rho^*_L,\rho^*_R) = u_L^* -u_R^* = 0,\\
%	f_\sigma(\rho^*_L,\rho^*_R) = \sigma_L^* -\sigma_R^* = 0,
%\end{aligned}
%\end{equation}
% use a Newton iteration method to  get new $\rho^*_L$ and $\rho^*_R$, then do steps 2-5 again until the result convergents. this process is given in Section \ref{sec:iteration}.
%\end{enumerate}

  \subsection{The solving process}\label{sec:iteration}
  By the relations in Section  \ref{sec:Riemann}, all  variables can be written as functions of  the density, so if  densities in regions $\mathbf{Q}^*_L$ and  $\mathbf{Q}^*_R$ are known, the Riemann problem is solved.

@@

\noindent  \textbf{Initial:}

@@

\noindent
\textbf{Iteration begin:}
\begin{enumerate}[Step 1]
  \item Case select:
	By a given  $\rho _{L,(k)}^*$ and a  $\rho _{R,(k)}^*$ in $k$ iteration step, we need to determine the case of the wave structures in the left and right. The determining  process is done in Section \ref{sec:deter}.

  \item Solving $f_u$ and $f_\sigma$:  After determining the structure case, we need  to solve the Cauchy stresses and the velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$, those are given in Section \ref{sec:functions}.

  \item  Updating  $\rho_L^*$ and $\rho_R^*$:   By the Newton iteration equation, new densities can be updated, 
\begin{equation}
\left[ \begin{array}{l}
 \rho _{L,(k+1)}^*\\
\rho_{R,(k+1)}^*\\
\end{array}
\right] = 
\left[ \begin{array}{l}
 \rho _{L,(k)}^*\\
\rho_{R,(k)}^*\\
\end{array}
\right]-
\left[ \begin{array}{ll}
\frac{\partial f_{u(k)}}{\partial \rho_L^*} & \frac{\partial f_{u(k)}}{\partial \rho_R^*}\\
\frac{\partial f_{\sigma(k)}}{\partial \rho_L^*} & \frac{\partial f_{\sigma(k)}}{\partial \rho_R^*}\\
\end{array}
\right]^{-1}
\left[ \begin{array}{l}
f_{u(k)}\\
f_{\sigma(k)}\\
\end{array}
\right]
\end{equation}
The derivatives of $f_{u}$ and $f_{\sigma}$ are given by
\begin{equation}
  \frac{\partial f_{u,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u,(k+1)}-f_{u,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},\quad
  \frac{\partial f_{\sigma,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{\sigma,(k+1)}-f_{\sigma,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},
\end{equation}
At the first step, we use a simple  numerical difference  method
\begin{equation}
  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},\quad
  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},
\end{equation}
where $\Delta \rho$ is a little quatity, we can choose it as
\begin{equation}
  \Delta \rho_{L(R)} = \frac{\rho_{L(R),(0)}^*}{100}.
\end{equation}
\item Convergence test:
The  convergence is meassured by 
\begin{equation}
\text{CHA} = \text{max} \left[  
\frac{|\rho_{L(k+1)}^*- \rho_{L,(k)}^*|}{\frac{1}{2}|\rho_{L(k+1)}^*+\rho_{L(k)}^*|},   \frac{|\rho_{R(k+1)}^*- \rho_{R,(k)}^*|}{\frac{1}{2}|\rho_{R(k+1)}^*+\rho_{R(k)}^*|},|f_{u}|,|f_{\sigma}|\right].
\end{equation}
and the tolerance is taken as $\text{TOL} = 10^{-4}$.

If $ \text{CHA} \le \text{TOL} $, the iteration ends. 
It usually takes 2-4 step to get a convergence result.
\end{enumerate}

\noindent
\textbf{Iteration end}
%\subsection{Pre-evaluation of densities}\label{sec:eva}
%At first, we assume that there are only one elastic shock wave in the left side and another one  elastic shock in the right side as shown in Fig.\ref{fig:HLLC}. According to the conservation relations across the shocks, we have    
%\begin{equation}
%  \left\{
%  \begin{aligned}
%	&\hat{\rho}_L\hat{u}^*_L = \rho_L u_L +s_L(\hat{\rho}_L^*-\rho_L), \\
%	&\hat{\rho}_L\hat{u}_L^{*2}-\sigma_L^* = \rho_L u_L^2 -\sigma_L +s_L(\hat{\rho}_L^* \hat{u}_L^*-\rho_L u_L), 
%  \end{aligned}
%\right.
%\end{equation}
%and
%\begin{equation}
%  \left\{
%  \begin{aligned}
%	&\hat{\rho}_R\hat{u}^*_R = \rho_R u_R +s_R(\hat{\rho}_R^*-\rho_R), \\
%	&\hat{\rho}_R\hat{u}_R^{*2}-\sigma_R^* = \rho_R u_R^2 -\sigma_R +s_R(\hat{\rho}_R^* \hat{u}_R^*-\rho_R u_R). 
%  \end{aligned}
%\right.
%\end{equation}
%\begin{figure}
%  \centering
%  \includegraphics[width=8cm]{Tikz-figure7.eps}
%  \caption{Pre-evaluation with a three-waves structure.}
%  \label{fig:HLLC}
%\end{figure}
%
%
%Using the relation across the interface,
%\begin{equation}
%  \hat{u}_L^* = \hat{u}_R^* =\hat{s}^*,\quad \hat{\sigma}_L^* = \hat{\sigma}_R^*.
%\end{equation}
%the speed of contact wave can be evaluated as 
%\begin{equation}
%\hat{s}^* = \frac{\sigma_L-\sigma_R+\rho_L u_L(s_L-u_L)-\rho_R u_R(s_R-u_R)}{\rho_L(s_L-u_L)-\rho_R(s_R-u_R)},
%\end{equation}
%the density is solved as 
%\begin{equation}
%\hat{\rho}_L^* = \frac{\rho_L(u_L-s_L)}{\hat{s}^*-s_L}, \quad
%\hat{\rho}_R^* = \frac{\rho_R(u_R-s_R)}{\hat{s}^*-s_R}.
%\end{equation}
%Here we define the speeds of left and right going waves as
% \begin{equation}
%      s_L = \text{min} (u_L-c_L, u_R-c_R, 0),  \quad s_R = \text{max}(u_L+c_L, u_R+c_R, 0).
%\end{equation}
\subsection{Determining the case of structures} \label{sec:deter}

@@

\subsection{States in  regions $\tilde{\mathbf{Q}}_{L}$ and   $\tilde{\mathbf{Q}}_{R}$}
 For cases (a,b,d,e) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, there is no midlle state $\tilde{\mathbf{Q}}_{L(R)}$. For  expression conveience, we let    
 \begin{equation}
   (\tilde{\rho}_{L(R)},\tilde{u}_{L(R)},\tilde{p}_{L(R)},\tilde{s}_{xx}) =(\rho_{L(R)}, u_{L(R)},p_{L(R)},s_{xxL(R)}),
\end{equation}

For cases (c,f), the meterial periods a yielding process from elastic to plastic. There are two waves and  one more state $\tilde{\mathbf{Q}}_{L(R)}$ exist. In state $\tilde{\mathbf{Q}}_{L(R)}$, the derivative stress achieves the elastic limit. 
\begin{equation}
 \tilde{s}_{xxL(R)} = \left\{ \begin{aligned}
	 &\frac{2}{3}Y_0 \quad  &\text{Case (c)},\\
	 &-\frac{2}{3}Y_0 \quad &\text{Case (f)},
	\end{aligned}
  \right.
\end{equation}
By  the relation in (\ref{eq:rhosxx}),  we can solve the density out as 
\begin{equation}
  \tilde{\rho}_{L(R)}= \left\{ \begin{aligned}
	  & \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (c)}, \\ 
	  & \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (f)}. 
	\end{aligned}
  \right.
	\end{equation}
	\emph{\textbf{Rarefaction wave case (c)}}
For rarefaction wave case,
we give the function of $s_{xx}$ at first,
\begin{equation}
  s_{xx}(\rho) =
	 -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}
  \end{equation}

The pressure is given as 
\begin{equation}
  p(\rho)=
	  p_{L(R)}e^{\frac{\lambda}{\rho_{L(R)}}-\frac{\lambda}{\rho}} +e^{-\frac{\lambda}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda}{x}}dx,\quad  \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},
\end{equation}
where 
\begin{equation}
  \lambda = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda\frac{s_{xx}(\rho)}{\rho^2}.
\end{equation}
